% This file is part of dirCompare
%
% Copyright 2017 Thomas Erbesdobler <t.erbesdobler@team103.com>
%
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.
%

% !TeX spellcheck = en_US
\documentclass[a4paper]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{color}

\title{Documentation for dirCompare}
\author{Thomas Erbesdobler $<$t.erbesdobler@team103.com$>$}
\date{Last updated: August 28, 2017}

\setlength{\parskip}{1ex}
\setlength{\parindent}{0pt}

\newenvironment{note}{\color{magenta}}{\normalcolor}

\begin{document}
	\maketitle
	\tableofcontents
	
	\section{What is dirCompare?}
	\label{sec:what_is_dircompare}
	
	''dirCompare'' is yet another open source tool for comparing directory trees. It is written in C++ and designed to be multi-platform with the capability to add more supported platforms quite easily. It is licensed under the Apache License, Version 2.0. The same license shall apply to this document, it shall be considered an object form of the \LaTeX{} code
	
	No initial release has been done yet, furthermore licensing information has still to be added.
	
	\section{User documentation}
	\label{sec:user_documentation}
	
	\subsection{Command line Parameters}
	\label{subsec:command_line_parameters}
	
	The following table lists all available command line parameters and their semantics:
	
	\begin{tabularx}{\linewidth}{l|X}
		\texttt{--help} & Show brief help and licensing information \\
		\texttt{--dir1 \textless path\textgreater} & Path to first directory for comparison \\
		\texttt{--dir2 \textless path\textgreater} & Path to second directory for comparison \\
		\texttt{--listStrategies} & List file and directory comparison strategies \\
		\texttt{--fileStrategy \textless id\textgreater} & Specify the comparison strategy for files \\
		\texttt{--dirStrategy \textless id\textgreater} & Specify the comparison strategy for directories \\
		\texttt{--ignoreFile \textless name\textgreater} & Ignore all files with the given name. This parameter might be specified multiple times. \\
		\texttt{--ignoreDir \textless name\textgreater} & Ignore all directories with the given name. This parameter might be specified multiple times. \\
		\texttt{--logfile \textless path\textgreater} & Use the specified log file. If none is given, the log output is written to \texttt{stdout} \\
	\end{tabularx}
	
	\subsection{Return code}
	\label{subsec:return_code}
	
	A return code of 0 signals an equality of the two directories in respect to the given comparison strategies. A different return code signals either their inequality or an error/failure like an invalid command line.
	
	\subsection{Comparison strategies}
	\label{subsec:comparison_strategies}
	
	Due to the internal structure of the system, the specified root directories are never filtered out, independent of the selected directory comparison strategy.
	
	\paragraph{Linux} The following file comparison strategies are currently available on the Linux platform:
	
	\begin{tabularx}{\linewidth}{lX}
		simple & Compares only the file parameters retrieved via \texttt{stat} except ctime, the count of allocated blocks and a few others. In case of a difference the reason is listed in the output log. However, not all inequalities are listed but only the first one compared and found unequal. This file comparison strategy performs no filtering, this has to be done by the used directory comparison strategy which is the only part of the system that can query files.
	\end{tabularx}

	\paragraph{Windows (Win32)} On Windows using Win32 API the following comparison strategies are currently available:
	
	It is important to note that System Access-Control Lists (SACLs) are currently not supported.
	
	\paragraph{All target platforms} The following directory comparison strategies are currently available on any target platform:
	
	\begin{tabularx}{\linewidth}{lX}
		simple & Compares only the directory content in a recursive manner. That is, two directories differ exactly if not all items are the same. Two items are equal if they are considered equal by the associated comparison strategy and additionally have the same name. Since the reason for inequality is always the difference of content, none is listed in the log. But if items are present in only one directory, this is listed and also in which one. This directory comparison strategy applies the set file- and directory filter in respect to the items included in the actual directory.
	\end{tabularx}
	
	\section{Licensing information}
	\label{sec:licensing_information}
	
	Copyright 2017 Thomas Erbesdobler $<$t.erbesdobler@team103.com$>$
	
	Licensed under the Apache License, Version 2.0 (the ''License'');
	you may not use this file except in compliance with the License.
	You may obtain a copy of the License at
	
	\begin{center}
		\url{http://www.apache.org/licenses/LICENSE-2.0}
	\end{center}
	
	Unless required by applicable law or agreed to in writing, software
	distributed under the License is distributed on an ''AS IS'' BASIS,
	WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
	See the License for the specific language governing permissions and
	limitations under the License.
	
\end{document}
